---
title: "Xin - UROP Analysis"
author: "Xin Lin"
date: "2024-04-01"
output: html_document
---

#Install packages
```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
library(table1)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(mediation)
library(lmtest)
library(lme4)
library(reshape2)
```

#Loading data
```{r}
data <- read.csv("C:/Users/xil90/OneDrive/Desktop/UROP Spring/Data/Xin UROP Coding.csv")
```

```{r}
clean_data <- na.omit(data[c("participant",
                             "finalClassGrade",
                             "caseStudy1",
                             "caseStudy2",
                             "caseStudy3",
                             "metacognition1ReflectQ4",
                             "metacognition1ReflectQ5", 
                             "metacognition2ReflectQ4",
                             "metacognition2ReflectQ5",
                             "metacognition3ReflectQ4",
                             "metacognition3ReflectQ5",
                             "metacognition1ConfidenceR",
                             "metacognition2ConfidenceR",
                             "metacognition3ConfidenceR",
                             "metacognition1ConfidenceStatistics",
                             "metacognition2ConfidenceStatistics",
                             "metacognition3ConfidenceStatistics",
                             "problemsolvingReflectionHelpful",
                             "problemsolvingReflectionunHelpful",
                             "problemSolvingReflectionStepbyStep"
                             )])
#clean the percentage in confidence
clean_data$metacognition1ConfidenceR <- as.numeric(gsub("%", "", clean_data$metacognition1ConfidenceR))
clean_data$metacognition1ConfidenceStatistics <- as.numeric(gsub("%", "", clean_data$metacognition1ConfidenceStatistics))

clean_data$metacognition2ConfidenceR <- as.numeric(gsub("%", "", clean_data$metacognition2ConfidenceR))
clean_data$metacognition2ConfidenceStatistics <- as.numeric(gsub("%", "", clean_data$metacognition2ConfidenceStatistics))

clean_data$metacognition3ConfidenceR <- as.numeric(gsub("%", "", clean_data$metacognition3ConfidenceR))
clean_data$metacognition3ConfidenceStatistics <- as.numeric(gsub("%", "", clean_data$metacognition3ConfidenceStatistics))

```

#Variable
##Final Class Grade
```{r}
grade <- clean_data$finalClassGrade
```
##Case Study Grade
```{r}
case1 <- clean_data$caseStudy1
case2 <- clean_data$caseStudy2
case3 <- clean_data$caseStudy3
```
###Total case studt score
```{r}
clean_data$TotalCaseStudyScore <- clean_data$caseStudy1 + clean_data$caseStudy2 + clean_data$caseStudy3
library(tidyverse)
#View(cbind.data.frame(clean_data$caseStudy1,clean_data$caseStudy2,clean_data$caseStudy3,clean_data$TotalCaseStudyScore))
```
##R confidence
```{r}
rc1 <- clean_data$metacognition1ConfidenceR
rc2 <- clean_data$metacognition2ConfidenceR
rc3 <- clean_data$metacognition3ConfidenceR
```
##Statistics confidence
```{r}
statc1 <- clean_data$metacognition1ConfidenceStatistics
statc2 <- clean_data$metacognition2ConfidenceStatistics
statc3 <- clean_data$metacognition3ConfidenceStatistics
```
##Mentacognitive reflection
```{r}
clean_data$mr1 <- (clean_data$metacognition1ReflectQ4 + clean_data$metacognition1ReflectQ5) 
mr2 <- (clean_data$metacognition2ReflectQ4 + clean_data$metacognition1ReflectQ5) 
mr3 <- (clean_data$metacognition3ReflectQ4 + clean_data$metacognition1ReflectQ5) 
pre_mr <-clea (clean_data$problemsolvingReflectionHelpful + clean_data$problemsolvingReflectionunHelpful + clean_data$problemSolvingReflectionStepbyStep)
```
###Total score of Metacognitive reflection
```{r}
TotalMRScore <- mr1 + mr2 + mr3
```
###Average Mentacognitive reflection
```{r}
AverageMR <- (mr1 + mr2 + mr3) / 3
```
###total confidence in R and Stat of each case
```{r}
confidence1 <- (clean_data$metacognition1ConfidenceR + clean_data$metacognition1ConfidenceStatistics) / 200
confidence2 <- (clean_data$metacognition2ConfidenceR + clean_data$metacognition2ConfidenceStatistics) / 200
confidence3 <- (clean_data$metacognition3ConfidenceR + clean_data$metacognition3ConfidenceStatistics) / 200
```
###total confidence
```{r}
TotalConfidence <- confidence1 + confidence2 + confidence3
```

#Histogram
```{r}
#Final class's scores
hist(grade, main = "Final Grade")

#Three case study's scores
hist(case1, main = "Final Score for Case Study 1")
hist(case2, main = "Final Score for Case Study 2")
hist(case3, main = "Final Score for Case Study 3")

#R confidence 
hist(rc1, main = "R confidence in case study 1")
hist(rc2, main = "R confidence in case study 2")
hist(rc3, main = "R confidence in case study 3")

#Statics confidence
hist(statc1, main = "Statistics confidence in case study 1")
hist(statc2, main = "Statistics confidence in case study 2")
hist(statc3, main = "Statistics confidence in case study 3")

#Metacognition reflects scores for each case study
hist(mr1, main = "Total Metacognition Reflect in case study 1")
hist(mr2, main = "Total Metacognition Reflect in case study 2")
hist(mr3, main = "Total Metacognition Reflect in case study 3")
hist(pre_mr, main = "Metacognition Reflect in problem solving reflection")

#total confidence
hist(TotalConfidence, main = "Total R and statistics confidence in three case study")

#total quality of metacogntion reflection score
hist(TotalMRScore, main = "Total R and statistics confidence in three case study")


```


#Analysis
#Descriptive Statistics
```{r}
summary(clean_data)
```

##Research Question #1:
Does student engagement with metacognitive reflection assignment association with student academic outcome?
###Analysis 1: Individual Reflection MR Scores
```{r}
model1 <- lm(grade ~ mr1 + mr2 + mr3, data = clean_data) 
summary(model1)

par(mfrow=c(2,2))
plot(model1)

```
This way?
```{r}
#overall
model1 <- lm(grade ~ TotalMRScore, data = clean_data)
summary(model1)

par(mfrow=c(2,2))
plot(model1)

ggplot(clean_data, aes(x=TotalMRScore, y=grade)) +
  geom_point() +
  geom_smooth(method="lm", color="blue") +
  labs(title="Relationship Between Metacognitive Reflection and Final Grade",
       x="Metacognitive Reflection Score", 
       y="Final Grade")
```

```{r}
#follow up: acoress three case study
# Prepare data for box plot
mr_data <- data.frame(
  CaseStudy1 = clean_data$mr1,
  CaseStudy2 = clean_data$mr2,
  CaseStudy3 = clean_data$mr3
)

melted_mr_data <- melt(mr_data, variable.name = "CaseStudy", value.name = "MRScore")

ggplot(melted_mr_data, aes(x = CaseStudy, y = MRScore)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "MR Scores Across Three Case Studies", x = "Case Study", y = "MR Score")
```

```{r}
boxplot(grade~TotalMRScore,
data=clean_data,
main="Different boxplots for each case study",
xlab="Month Number",
ylab="Degree Fahrenheit",
col="orange",
border="brown"
)

ggplot(data = clean_data) + 
  geom_point(mapping = aes(x = TotalMRScore, y = grade))
ggplot(data = clean_data) + 
  geom_smooth(mapping = aes(x = TotalMRScore, y = grade))
```

###Analysis 2: Using Average Reflection Score *
```{r}
model2 <- lm(grade ~ avgmr, data = clean_data)
summary(model2)

par(mfrow=c(2,2))
plot(model2)
```

##Research Question #2:
How does student’s reflections on pre-course metagecontion reflection assignment association with their performance in first exam?

###Analysis3
```{r}
model3 <- lm(case1 ~ premr, data = clean_data)
summary(model3)

par(mfrow=c(2,2))
plot(model3)

ggplot(clean_data, aes(x=premr, y=case1)) +
  geom_point() +
  geom_smooth(method="lm", color="red") +
  labs(title="First Exam Scores by Pre-Course Metacognition Reflection Level",
       x="Pre-Course Reflection Level", 
       y="First Exam Score")
```

##Research Question #3:
Does students’ confidence levels in statics and R programming predict their performance in the performance (exam) in the course?

```{r}
model4 <- lm(case1 ~ confidence1, data = clean_data)
summary(model4)

par(mfrow=c(2,2))
plot(model4)
```
```{r}
model6 <- lm(case2 ~ confidence2, data = clean_data)
summary(model6)

par(mfrow=c(2,2))
plot(model6)
```
```{r}
model7 <- lm(case3 ~ confidence3, data = clean_data)
summary(model7)

par(mfrow=c(2,2))
plot(model7)
```

```{r}
confidence_data <- data.frame(
  CaseStudy1 = clean_data$metacognition1ConfidenceR,
  CaseStudy2 = clean_data$metacognition2ConfidenceR,
  CaseStudy3 = clean_data$metacognition3ConfidenceR
)

melted_confidence_data <- melt(confidence_data, variable.name = "CaseStudy", value.name = "Confidence")

ggplot(melted_confidence_data, aes(x = CaseStudy, y = Confidence)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Confidence Level Across Three Case Studies", x = "Case Study", y = "Confidence Level")
```

#Anova analysis?
##the confidence change acoress three case study
```{r}
data_long <- data.frame(
  ParticipantID = rep(clean_data$participant, times = 3),
  TimePoint = rep(1:3, each = nrow(clean_data)),
  Confidence = c(
    (clean_data$metacognition1ConfidenceR + clean_data$metacognition1ConfidenceStatistics) / 2,
    (clean_data$metacognition2ConfidenceR + clean_data$metacognition2ConfidenceStatistics) / 2,
    (clean_data$metacognition3ConfidenceR + clean_data$metacognition3ConfidenceStatistics) / 2
  )
)
```

```{r}
data_long$TimePoint <- as.factor(data_long$TimePoint)


anova_results <- ezANOVA(
  data = data_long,
  dv = .(Confidence),
  wid = .(ParticipantID),
  within = .(TimePoint),
  detailed = TRUE,
  type = 3
)

anova_results

```

